---
title: "A009 and A010 DQ Checks"
author: "NCCES_tim_bender"
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries and functions, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(data.table)
library(readr)
library(glue)
library(crayon)

funA010 <- function(sum.data, 
                  provider.prompt, 
                  username){
  require(readr)
  temp.pp <- provider.prompt %>% trimws()
  temp.pid <- temp.pp %>%
    strsplit(., split = "\\(|\\)$") %>%
    unlist() %>%
    as.numeric() %>%
    .[!is.na(.)]
  temp.uid <- username %>%
    strsplit(., " ") %>%
    unlist() %>%
    strsplit(., "")
  if(length(temp.uid) == 2){
    temp.uid <- temp.uid %>%
      lapply(., first) %>%
      unlist() %>%
      tolower() %>%
      paste(., sep = "", collapse = "")
  
  }else{
    temp.uid <- temp.uid %>% 
      unlist() %>%
      tolower() %>%
      paste(., sep = "", collapse = "") %>%
      substr(., 0, 2)
  }
  temp.uid <- paste(temp.pid, temp.uid, "A010", sep = "_", 
                    collapse = "_")
    
  
  sum.df <- read_tsv(sum.data, 
                     col_names = c("variable", "value"))
  sum.df$value <- gsub("\\(", "-", sum.df$value) %>%
    gsub("\\)|,", "", .) %>%
    as.numeric()
  #sum.df$project_id <- temp.pid
  sum.df$uid <- temp.uid
  
  out.df <- sum.df %>% as.data.table()
  return(out.df)
}
```


## OVERVIEW
Download A009 and A010 Report with the specifications listed below.  The pull up the PATH dashboard (not a report; just a dashboard in HMIS) and compare them the A0XX reports to the dash and see where the differences are and log them.

#### GitHub Links:
* Project Website (i.e. this document): https://timbender-ncceh.github.io/A009_A010_dq/
* Repository: https://github.com/timbender-ncceh/A009_A010_dq/tree/main
* Projet Issues / Comments: https://github.com/timbender-ncceh/A009_A010_dq/issues

#### ZenGuide Links:
* ZenGuide_General: https://ncceh.zendesk.com/
* A009: https://ncceh.zendesk.com/hc/en-us/articles/16245113253523-A009-PATH-Details-Data-Quality-Report-Guide
* A010: https://ncceh.zendesk.com/hc/en-us/articles/16273061844883-A010-PATH-Services-Referrals-Report-Guide
* PATH_Dashboard: https://ncceh.zendesk.com/hc/en-us/articles/15097522537235

## PROJECT HOW-TO 

#### From Login 
* Shadow user [redacted] or [redacted]
* Connect to BusinessObjects

#### Folder Directory 
* See ZenGuide

#### Query Setup
* See ZenGuide for filetype and output directions
* Click the three dot symbol (…)(⋯) not the name of the report to set it up and run it.  This allows for report configuration. 
* You will need to select one provider_id (see notes below) and compare to PA

<!-- #### QA Steps, Tabled  -->

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
tbl1 <- expand.grid(report = c("A009", "A010"), 
            #comparison = "PATH_dash",
            start_date = "07-01-2022",
            end_date   = "06-30-2023",
            notes = "SSO+SO+PATH",
            pid = sort(c(20538, 20539, 
                            20478, 20477))) %>%
  as.data.table()

tbl2 <- data.frame(uid = NA, 
                   pid = tbl1$pid, 
                   shadow_user = c(rep("michele knapp", 4), 
                                   rep("benjamin horton", 4)))
out1 <- full_join(tbl2,tbl1) %>%
  .[!duplicated(.),]

rownames(out1) <- 1:nrow(out1)

out1$uid <- paste(out1$pid, 
                  # paste(substr(out1$pid,
                  #       start = nchar(out1$pid)-2, 
                  #       stop = nchar(out1$pid)), 
      unlist(lapply(lapply(strsplit(out1$shadow_user, " "), 
         substr, start = 1, stop = 1), 
         paste, sep = "", collapse = "")), 
      out1$report,
      sep = "_") 

print(out1)

```

## REPORT REVIEW
### A009
#### Report Data:
#### Review Steps:
  * [To be included from ZenGuide Report]
  
### A010
#### Report Data:
```{r A010 Data, echo=FALSE, message=FALSE, warning=FALSE}

da010 <- funA010(sum.data = "Total Clients with Project Entry/Exit	185 
Total Clients with Services	152 
Total Services	572 
Total Clients with Referrals	19 
Total Referrals	41 
Total Clients with PATH enrollment	19 
Total PATH enrolled Clients with Services	20 
Total PATH enrolled Clients without Services	(1)
Total PATH enrolled Clients with Referrals	14 
Total PATH enrolled Clients without Referrals	5 
", 
                 provider.prompt = "Diakonos, Inc. - Iredell County - Street Outreach - SO - PATH(20477)", 
                 username = "michele knapp")
print(da010)

```


#### Review Steps:
* Confirm the total clients with a project entry/exit appears accurate for the number of clients served/contacted during the reporting period.  
  - [Line 1] == [?]
```{r echo=FALSE, message=FALSE, warning=FALSE}
cat(glue("{da010$value[1]} == [\"???\"]"))
da010$value[1] == NA
```
  
* Confirm the number of clients marked as PATH enrolled appears accurate.  
  - [Line 6] == [?]
```{r echo=FALSE, message=FALSE, warning=FALSE}
cat(glue("{da010$value[6]} == [\"???\"]"))
da010$value[6] == NA
```  
* The total clients with PATH enrollment should equal the "total PATH enrolled clients with services" + "total PATH enrolled clients without services".  
  - [Line 6] == [Line 7] + [Line 8]
  - If the numbers do not add up, you will want to check for duplicate/dual enrollments (the same client served more than once during the reporting period). 
```{r echo=FALSE, message=FALSE, warning=FALSE}
cat(glue("{da010$value[6]} == {da010$value[7]} + {da010$value[8]}\n{da010$value[6] == da010$value[7] + da010$value[8]}"))
```

* The total clients with PATH enrollment should also equal the "total PATH enrolled clients with referrals" + "total PATH enrolled clients without referrals".  
  - [Line 6] == [Line 9] + [Line 10] 
  - If the numbers do not add up, you will want to check for duplicate/dual enrollments (the same client served more than once during the reporting period).
```{r echo=FALSE, message=FALSE, warning=FALSE}
cat(glue("{da010$value[6]} == {da010$value[9]} + {da010$value[10]}\n{da010$value[6] == da010$value[9] + da010$value[10]}"))

```
 

### QA FINDINGS
[to be completed]

#### Current Status
```{r A010 status, echo=FALSE, message=FALSE, warning=FALSE}
tbl010_status <- out1[out1$report =="A010",c("uid","pid")] %>%
  mutate(., 
         report_dl = F, 
         QA_comp   = F) %>%
  .[!colnames(.) %in% "pid"]
print(tbl010_status)
```



#### Identified QA Issues


## CONCLUSION 


```{r Silent Chunk to copy html output to clipboard, message=TRUE, warning=TRUE, include=FALSE}
# library(htmltools)
# library(utils)
# writeClipboard(str = includeHTML("a009_a010.html"))

if(file.exists("a009_a010.html")){
  file.rename(from = "a009_a010.html", 
            to = "index.html")
}


```

